Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-10 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:10	10:46:42	(Mon10.Aug)
la2pdf commit - 2015:08:10	14:21:12	(Mon10.Aug)

As will be demonstrated in upcoming sections, the LCA beamformer works very well with windows generated from the Kaiser-Bessel function. It is defined as:
%
\begin{align}
w_m = \begin{cases}
\frac{I_0\left(\pi\beta\sqrt{1-\left(\frac{m}{M/2}\right)^2}\right)}{I_0(\pi\beta)}, & 0\le |m|\le M/2 \\
0 & \text{otherwise}
\end{cases}
\end{align}
%
where $I_0$ is the zeroth order Modified Bessel function of the first kind, defined as:
%
\begin{align}
I_0(x) = \sumb{k=0}{\infty} \left[ \frac{\left(\frac{x}{2}\right)^k}{k!} \right].
\end{align}
%

As will be demonstrated in upcoming sections, the performance of the LCA beamformer is surprisingly similar regardless of what windows it is allowed to choose from. Therefore we have selected a 
% 
% 
% α controls the tradeoff between main-lobe width and side-lobe area.  As α increases, the main lobe of W0(f) increases in width, and the side lobes decrease in amplitude, as illustrated in the figure at right.  α = 0 corresponds to a rectangular window. For large α, the shape of the Kaiser window (in both time and frequency domain) tends to a Gaussian curve.  The Kaiser window is nearly optimal in the sense of its peak's concentration around frequency 0 (Oppenheim et al., 1999).
% 
% Narrow ones:
% - Best coherent gain, lowest equivalent noise bandwidth, and most sensitive to steering meaning not needing to steer as much for some effect.
% 
% 
% Beamforming:
% - Maximize resolution
% - Minimize noise/error, both coherent and incoherent
% - Minimize signal cancellation
% 
% Gauss: Miminized time-bandwidth product
%   - 
%   
% Rectangular
%   - 
% Dolph-Cheb: Minimize mainlobe width given sidelobe suppression
% Kaiser: For a restricted energy and time duration, maximize energy in the band of frequencies W.
% 
% Adaptive windows perform best in detection of closely separated angles of significantly amplitudes.

% \begin{figure}[p]\centering%
% \subfloat[Image of a single speckle realisation.]{%
% \includegraphics[width=\linewidth]{gfx/img_das_lca_mv.pdf}%
% \label{speckleA}}%
% % \hfil%
% \subfloat[Mean image of 100 speckle realisations.]{%
% \includegraphics[width=\linewidth]{gfx/img_das_lca_mv_mean100.pdf}%
% \label{speckleB}}%
% \caption{A simulated circular object buried in speckle is imaged from above.}\label{speckle}
% \end{figure}

% 
% 
% \begin{figure}[tp]\centering%
% \subfigure{%
% \graphicsAI[width=\linewidth]{gfx/img_das_lca_mv.pdf}}
% \subfigure{%
% \graphicsAI[width=\linewidth]{gfx/img_das_lca_mv_mean100.pdf}}%
% \caption{A simulated circular object buried in speckle is imaged from above.\newline\parbox[t]{1.50cm}{Top:\newline Bottom:}\parbox[t]{6.8cm}{Image of a single speckle realisation.\newline Mean image of 100 speckle realisations.}}\label{speckle}%%
% \end{figure}%
% 
% \begin{figure}[t]\centering%
% \graphicsAI[width=\linewidth]{gfx/img_mean_cut.pdf}%
% \caption{Lateral cut in the mean image at range 41.1\,m (highlight) and 44.5\,m (shadow).}\label{cutmean}%
% \end{figure}
% % \begin{figure}[t]\centering
% % % \graphicsAI[drawing,width=\linewidth]{gfx/the_box.svg}\\
% % \includegraphics[width=\linewidth]{gfx/selected_windows.pdf}
% % \caption{Selected windows}\label{selected_windows}
% % \end{figure}
% % \begin{figure}[t]\centering
% % \includegraphics[width=\linewidth]{gfx/selected_windows_angle.pdf}
% % \caption{Selected windows - Colored by angle}\label{selected_windows_angle}
% % \includegraphics[width=\linewidth]{gfx/selected_windows_sym_angle.pdf}
% % \caption{Selected windows - Colored symmetrically by angle}\label{selected_windows_sym}
% % \end{figure}
% \begin{figure}[t]\centering
% \graphicsAI[width=\linewidth]{gfx/img_holmengraa.pdf}%
% \caption{HISAS sidescan sonar (SSS) image of the shipwreck Holmengraa.}\label{holmengraa}%
% \end{figure}

@@

hmm

>>>>

As will be demonstrated in upcoming sections, the LCA beamformer works very well with windows generated from the Kaiser-Bessel function. It is defined as:
%
\begin{align}
f_m = \begin{cases}
\frac{I_0\left(\pi\beta\sqrt{1-\left(\frac{2m}{M-1}-1\right)^2}\right)}{I_0(\pi\beta)}, & 0\le m\le M-1 \\
0 & \text{otherwise},
\end{cases}
\end{align}
%
where $I_0$ is the zeroth order Modified Bessel function of the first kind:
%
\begin{align}
I_0(x) = \sumb{a=0}{\infty} \left[ \frac{\left(\frac{x}{2}\right)^a}{a!} \right]^2.
\end{align}
%
The Kaiser-Bessel window is near optimal in the sense of having its peak energy concentration around $\theta=0^\circ$, for a time-bandwidth product specified with the parameter $\beta$:
%
\begin{align}
\beta = \frac{TB}{2},
\end{align}
%
where $T$ is the extent of the window in time and $B$ is its bandwidth. Adjusting $\beta$ changes the trade-off between mainlobe width and sidelobe level. At small values the windows approach the response of a rectangular window, and at large values ($>5$) the window converges to a Gaussian both in time and frequency. This class of windows is generally considered well suited for separating closely spaced sources with amplitudes of a high dynamic range~\cite{Harris1978}.

Before we apply the window to the sensor data, we normalize it to ensure unit gain in the direction of interest:
\begin{align}
\w = \frac{\vec f}{\vec f\T\1} \quad\quad\text{where}\quad\quad \vec f =
\bmat{
f_0 \\ \vdots \\ f_{M-1}                                                           
}
\end{align}

Note that the normalization factor is the reciprocal of the window's coherent gain.

% 
% Narrow ones:
% - Best coherent gain, lowest equivalent noise bandwidth, and most sensitive to steering meaning not needing to steer as much for some effect.
% 
% 
% Beamforming:
% - Maximize resolution
% - Minimize noise/error, both coherent and incoherent
% - Minimize signal cancellation
% 
% Gauss: Miminized time-bandwidth product
%   - 
%   
% Rectangular
%   - 
% Dolph-Cheb: Minimize mainlobe width given sidelobe suppression
% Kaiser: For a restricted energy and time duration, maximize energy in the band of frequencies W.
% 
% Adaptive windows perform best in detection of closely separated angles of significantly amplitudes.

@@

% the performance of the LCA beamformer is surprisingly similar regardless of what windows it is allowed to choose from.
